Robust receding horizon control for linear systems with state dependent disturbance

### 2015-04-20 draft_v2.tex
edited sections 1-3

\section{Introduction}\label{sec:intro}
Robust model predictive control (RMPC) algorithms compute a control law optimising a performance
criterion subject to state and control constraints for a perturbed system, for all possible realisations of the
perturbation. \cite{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary 
tries to maximise the effect of the uncertainty on the cost and the controller chooses its strategy to minimise 
the cost for the worst case system, this formulation is widely accepted, see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.
The worst case system can either be considered to be open-loop, i.e. the controller chooses its strategy for the 
whole horizon before the adversary decides its strategy, or closed-loop, i.e. at each stage along the horizon 
the controller and the adversary play the game for only that stage given the outcome of the previous stage.
Theoretical properties of these controllers are well understood, see e.g.~\cite{Mayne:2000}. However, the
numerical computation of robust model predictive controllers still poses a challenge and only few tractable 
solutions have been proposed.

Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
input constraints and linearly constrained additive uncertainty.
\NOTE{Do we need to constrain ourselves to additive here? In the literature there are algorithms that cope with
multiplicative just as well..?!}
\cite{Scokaert:1998} propose a scenario-based approach to solve the sequence of min-max problems, however the
complexity grows exponentially with the length of the horizon. A parametrised algorithm was proposed by~\cite{Rakovic:2012}
which can be used to reduce the RMPC problem to a single linear program that can be solved online, bit this 
parametrisation is in general suboptimal. Explicit RMPC algorithms solve the min-max problems offline and exploit 
the structure of the solution using results from multi-parametric programming to parametrise the optimal feedback as 
piecewise affine functions of the state, see e.g.~\cite{Bemporad:2003,Diehl:2004}. However, this requires extensive offline
computation and becomes inefficient for a high dimensional state space. Another approach exploiting the structure
of the solution in the same way but with less redundancy was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC},
where an active set solver is designed to solve the sequence of min-max problems explicitly online. In all 
aforementioned papers and, to the authors' best knowledge, in published literature on algorithmic solutions to the RMPC 
problem, the disturbance sets are assumed to be constant, i.e. independent of the system state and control inputs.
Recent algorithmic advances allow us to treat polytopic disturbance sets which depend in an affine way on the system state
and the control input. \cite{Schaich:2015} provide an algorithmic and analytical framework to
embed affine state and input dependent disturbance constraints into the framework of the active set RMPC solver
framework as proposed by~\cite{Buerger:2011}. Disturbance constraints varying with the state and input can be used
to model multiplicative uncertainty as well as linearisation errors which will be shown in an example.

After describing the considered control problem in section~\ref{sec:problem:statement} we summarise preliminary 
results which are necessary to formulate the considered problem explicitly (section~\ref{sec:preliminaries}).
Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
the essential parts of the active set solver, it is applied to the considered min-max problem in section~\ref{sec:applied:mpQP}
assuming the active set of constraints is known. A line search to determine the active set of constraints is presented
in section~\ref{sec:line:search}, the application of the proposed algorithm to an example system is presented in 
section~\ref{sec:example}. Conclusions are given in section~\ref{sec:conclusion}.

\section{Problem Statement}\label{sec:problem:statement}
The set of systems to which a min-max robust receding horizon control scheme can be applied online 
without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
adopt here, is to use the structure of the solution and derive multi-parametric programs that can be solved 
efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation 
formulations have to be available, in particular we consider linear constraints. In presence of state constraints 
the algorithmic treatment of state constraints in min-max problems stagnated after it was introduced for fixed 
polytopic disturbance sets by~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the
so called maximal robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state 
and input dependent disturbance constraints is presented. In this paper we develop the algorithm even further allowing 
us to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We present a 
robust receding horizon control scheme for
%
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x, x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ the input and $w\in\mathcal W(x,u)
\subset\mathbb R^q$ the disturbance with the state and input dependent disturbance set $\mathcal W(x,u)$. The disturbance 
set $\mathcal W(x,u)$ is defined by
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where $H(x,u)$ is an element-wise convex piecewise affine function. The min-max optimal control problem
we will optimise is given by the $N$-stage min-max program
%
\begin{subequations}\label{eq:the:problem}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w\\
	u\in\mathcal U \\
	w\in\mathcal W(x,u) \\
	(x,u)\in\mathcal Z_m
\end{gather}
\end{subequations}
%
where we enforce the stage wise state and input constraints $\mathcal Z_m$ in such a way that the terminal state,
i.e. $x^+$ at $m=1$, is contained in the MRPI set $x^+\in\mathcal X^\infty$ for the closed-loop 
system governed by a fixed state feedback controller $u=Kx$. The MRPI set $\mathcal X^\infty$ for this considered
scenario is therefore given by
%
\begin{equation}\label{eq:definition:MRPI:set}
	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\}.
\end{equation}
%
subsequently the stage wise constraints $\mathcal Z_m$ are defined recursively as
%
\begin{subequations}\label{eq:definition:stage:constraints}
\begin{align}
	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
	\label{eq:definition:mixed:stage:constraint}\\
	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
	\label{eq:definition:state:stage:constraint}\\
	\mathcal X_0 &= \mathcal X^\infty
\end{align}
\end{subequations}

\section{Preliminaries}\label{sec:preliminaries}
In this section we summarise preliminaries necessary to formulate the considered problem~\eqref{eq:the:problem}
in a convenient way. The point-wise polytopic set defined by~\eqref{eq:PWA:def:disturbance} with a elementwise convex 
piece-wise affine right-hand-side $H$ can be shown to lead to a polytopic MRPI set, see~\cite{Schaich:2015} for an 
elaborate discussion. We summarise the result as we require it in
%
\begin{lem}\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ polyhedral, and the pair $(A+BK,\Gamma)$ be
observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{lem}
%
We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
Notice that one essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex~$w_k(x,u)$ is a piecewise affine function in $(x,u)$,i.e.
\begin{equation}
\Resize{
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1},W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
}
\end{equation}
where the maximisation is done elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}, the recursion~\eqref{eq:definition:mixed:stage:constraint}
therefore defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\Resize{
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap\\
	&\{(x,u):\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i} \forall w\in\mathcal W(x,u),i\in\mathcal I_0\}\\
	=&(\mathbb R^n\times\mathcal U)\cap\\
	&\left\{\vphantom{\max_{w}}\right.
	(x,u):\max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i}\forall i\in\mathcal I_0
	\left.\vphantom{\max_w}\right\}\\
	=&(\mathbb R^n\times\mathcal U)\cap\\
	&\left\{\vphantom{\max_{w}}\right.
	\Lambda_{0,i}(Ax+Bu)+ \underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(I)}\leq\lambda_i\forall i\in\mathcal I_0
	\left.\vphantom{\max_w}\right\}
\end{aligned}
}
\end{equation}
The maximisation~$(I)$ in~\eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine. Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, its projection~$\mathcal X_1$ 
onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

>>>>

\section{Introduction}\label{sec:intro}

Robust model predictive control (RMPC) algorithms compute a control law that optimises a predicted performance
criterion subject to state and control constraints for all possible realisations of model
uncertainty. \citet{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary
tries to maximise the effect of model uncertainty on the cost and the controller chooses its strategy to
minimise the cost for the worst case system parameters and disturbances. This formulation is widely accepted
in the RMPC literature \citep[e.g.][]{Bemporad:1999,Bemporad:2003,Lee:1997}.
%see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.  
The predicted control law may be an open-loop policy, in which case the controller chooses its strategy for
the whole prediction horizon before the adversary decides its strategy, or a closed-loop policy in which the
horizon is split into stages and the actions of controller and adversary at each stage depend on the
outcome of the previous stage). Theoretical properties of these controllers are well understood \citep[e.g.][]{Mayne:2000}. However, the numerical computation of robust model predictive controllers still poses
a challenge and only few tractable solutions have been proposed.

Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
input constraints, with model uncertainty in the form of bounded additive disturbances and/or multiplicative
parameters. For the case of unknown additive disturbances, \citet{Scokaert:1998} propose a scenario-based
approach to solve a sequence of min-max problems online, however the computational complexity of this approach
grows exponentially with the length of the horizon. A parametrised algorithm was proposed
by~\cite{Rakovic:2012} which reduces the RMPC problem to a single linear program to be solved online, but
although this is a closed loop strategy the parametrisation is in general suboptimal. Explicit RMPC algorithms
optimise the worst case predicted performance for each admissible model state offline and
%exploit the structure of the solution using results
use results from multi-parametric programming to parametrise the optimal control law as a piecewise affine function of the
state \citep[e.g.][]{Bemporad:2003,Diehl:2004}. However, this requires extensive offline computation and
becomes inefficient for a high-dimensional state space.
An alternative approach that similarly exploits the piecewise affine structure of the solution, but with
less redundancy, was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC}. In this work an active set
solver is designed to solve a sequence of min-max problems explicitly online.

In all of this work and, to the authors' best knowledge, in all of the published literature on algorithmic
solutions to the RMPC problem, the disturbances are confined to sets that are assumed to be constant,
i.e.~independent of the system state and control inputs. Recent algorithmic advances~\citep{Schaich:2015}
make it possible to treat polytopic disturbance sets that depend in an affine manner on the system state and the control
input. This provides an algorithmic and analytical framework which is used in the
current paper to embed affine state and input dependent disturbance constraints into the framework of the
active set RMPC solver framework proposed by~\cite{Buerger:2011}. Disturbances that belong to sets which depend
on model states and inputs can account for multiplicative model uncertainty as well as linearisation
errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.
%, as will be shown in an example.

After describing the control problem in Section~\ref{sec:problem:statement} we summarise preliminary 
results which are necessary to formulate the considered problem explicitly (Section~\ref{sec:preliminaries}).
Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
the essential parts of the active set solver, and this is applied to the min-max RMPC problem in Section~\ref{sec:applied:mpQP}
for the case that the active set of constraints is known. A line search to determine the active set of constraints is presented
in Section~\ref{sec:line:search}. The application of the proposed algorithm to an example problem is presented in 
Section~\ref{sec:example} and conclusions are drawn in Section~\ref{sec:conclusion}.

\section{Problem Statement}\label{sec:problem:statement}
We consider a computationally efficient method for solving online min-max receding horizon control problems
that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
feedback law without approximating the cost or the constraints of the problem, and without making restrictive
assumptions on the parametrisation of control inputs.
%This broadens the applicability of the approach, allowing for higher order models and longer
%prediction horizons than 
%
%The high computational complexity of online min-max receding horizon control schemes generally requires either
%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
%solutions.
%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
%formulations have to be
%The algorithmic treatment of min-max problems
%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
%input dependent disturbance constraints. In this paper we develop the algorithm further
%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
%present a robust receding horizon control scheme for
%
To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
linear-quadratic problem formulation. Thus we assume the linear dynamic model 
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ is the control input
and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input. The disturbance set $\mathcal
W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where $H(x,u)$ is an elementwise convex, piecewise affine function. The control objective is to minimize the
worst case value, over all future model uncertainty, of the cost
\begin{equation}\label{eq:quadratic:cost}
\sum_{k=0}^\infty \bigl( \|x_k\|_Q^2 + \|u_k\|_R^2 - \gamma^2 \|w_k\|^2 \bigr) ,
\end{equation}
where the subscript $k$ denotes the realisation of a variable at time $k$, $\|x\|_Q^2$ denotes the quadratic
form $x^TQx$, $Q$ and $R$ are given positive definite
matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
disturbance sequence to the state and control sequences.

Given a prediction horizon of $N$ steps over which the predicted control law is to be optimized, we define the
min-max optimal control problem with $m$ stages to go as
%
\begin{subequations}\label{eq:the:problem}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w\\
	u\in\mathcal U \\
	w\in\mathcal W(x,u) \\
	(x,u)\in\mathcal Z_m
\end{gather}
\end{subequations}
%
for $m=1,\ldots,N$, with $J_0^\ast(x) = \|x\|_{P_0}^2$.
The stagewise  state and input constraints $\mathcal Z_m$ are defined recursively by
%
\begin{subequations}\label{eq:definition:stage:constraints}
\begin{align}
	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
	\label{eq:definition:mixed:stage:constraint}\\
	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
	\label{eq:definition:state:stage:constraint}\\
\end{align}
with
\begin{equation}
	\mathcal X_0 = \mathcal X^\infty .
\end{equation}
\end{subequations}
Thus the constraints $(x,u)\in\mathcal Z_m$ ensure that the terminal state, namely $x^+$ at $m=1$, is
contained in $\mathcal{X}^\infty$. We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
$u=Kx$, so that 
%
\begin{equation}\label{eq:definition:MRPI:set}
	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\},
\end{equation}
%
and we define $P_0$ so that $J_0^\ast(x)$ is the worst case value of the cost (\ref{eq:quadratic:cost}) under
$u=Kx$ in the absence of constraints.
Recently~\cite{Schaich:2015} proposed an algorithm to compute MRPI sets
for linear systems subject to state and input dependent disturbance constraints. In this paper we combine this approach
with the multistage multi-parametric programming method of~\cite{Buerger:ACC} to derive an efficient algorithmic
solution to the online MPC optimization of (\ref{eq:the:problem}a-e).

\section{Controllable sets}\label{sec:preliminaries}
In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} to be to formulated
in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) associated
with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex and
piecewise affine. For a proof and detailed discussion of this result we refer the reader
to~\cite{Schaich:2015}.
%
\begin{lem}\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be polyhedral, and the pair $(A+BK,\Gamma)$ be
observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{lem}
%
We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
Note that an essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
\begin{multline}
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
\end{multline}
where the maximisation is performed elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
& \!\!\!\!\!\!
\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
	\Bigr\} \end{aligned}
\end{aligned}
\end{equation}
Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine in $(x,u)$. 
Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
of $\mathcal Z_1$ onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.
